extracting mean profiles

### 2016-04-07 mean-profiles.Rmd
the rollapply seems to do a reasonable job for estimating the twist

@@

gg115$modeltwist <- predict(m115, newdata=gg115)
# round to precision of y:
gg115$roundtwist <- 1.5625*round(gg115$modeltwist/1.5625, 0)

@@

>>>>

Rs <- data.frame(zoo::rollapply(data=dframe$twist, width=200, FUN=function(twist) {
  x <- 1:length(twist)
  m <- lm(twist~x)
  data.frame(r.squared=summary(m)$r.squared, twist=coef(m)[2])
}, by=1))

twist <- median(subset(Rs, r.squared > .8)$twist)

@@

gg115$modeltwist <- predict(m115, newdata=gg115)
gg115$modeltwist2 <- gg115$x*twist
# round to precision of y:
gg115$roundtwist <- 1.5625*round(gg115$modeltwist/1.5625, 0)
gg115$roundtwist2 <- 1.5625*round(gg115$modeltwist2/1.5625, 0)

@@

qplot(y-roundtwist2, x, fill=resid, data=gg115, geom="tile") + scale_fill_gradient2(limits=c(-7,7))
